### 2017-11-12 Draft2/Intro.tex
Follow STS guidelines. Polish the intro.

In this paper, I introduce an alternative data structure to the dynamic array, called the \textbf{growth array}. It is more efficient than the dynamic array at appending large numbers of items. This is due to how it 'grows' once it cannot fit more items in its buffer.

When dynamic arrays run out of space, they allocate a new buffer, copy the contents of the old one into it, and throw the old one away. However, growth arrays are less wasteful. Instead of throwing away the filled buffer, they keep it a part of the data structure. The new buffer they allocate represents a continuation of the items from the old buffer. For example, if the old buffer contained items $0 - 31$, the new buffer would contain items $32$ and beyond. Because of this, growth arrays allocate less memory to store the same number of items, and they do not need to copy items from the old buffer to the new one.

Growth arrays have caveats, however. They perform no better, or slightly worse, than dynamic arrays for operations other than appending. Random access, in particular, involves many more instructions than it does for dynamic arrays. Also, since growth arrays are not contiguous in memory, they may have poorer locality than dynamic arrays, and cannot be passed to external code that accepts contiguous buffers.

It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are completely unnecessary. A raw array could simply be allocated with the known size, and items could be appended to it just as quickly. Thus, growth arrays are only beneficial for cases where the amount of data to be appended is unknown, but is expected to be large.

>>>>

In this paper, I introduce an alternative data structure to the dynamic array, called the \textbf{growth array}. It is more efficient than the dynamic array at appending large numbers of items. This is due to how it `grows' once it cannot fit more items in its buffer.

When dynamic arrays run out of space, they allocate a new buffer, copy the old one's contents into it, then throw the old one away. Growth arrays are less wasteful in this scenario. Instead of discarding the filled buffer, they simply archive it. The new buffer they allocate represents a continuation of the items from the old buffer. For example, if the old buffer contained items $0 - 9$, the new buffer would contain items $10$ and beyond. Because of this technique, growth arrays allocate less memory to store the same number of items, and do not need to copy the contents of old buffers.

Growth arrays have caveats, however. For operations other than appending, they perform no better, or slightly worse, than dynamic arrays. In particular, random access is very costly for growth arrays. They are also not contiguous in memory, which gives them poorer locality than dynamic arrays, and prevents them from being passed to external code that accepts contiguous buffers.

It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are redundant. One could simply allocate a raw array with the known size, and append items to it just as quickly. Thus, growth arrays are only beneficial for cases where the amount of data to be appended is unknown, but is expected to be large.
